Individual and Differential Harm in Redistricting

### 2022-08-27 paper/harm.Rmd
Update harm.Rmd

We formalize and generalize the concepts in Section \ref{sec:motivation}, beginning with some notation.
Let $\Voters$ be the set of individuals, or voters, in the region and time period under consideration, who vote to select a candidate to represent each of a set of districts, indexed by $\Distrs$.

@@

Every voter resides in some legislative district; this assignment is referred to as a *districting plan* and is represented here by a function $q(i)$ indicating the district that individual $i$ lives in.
The set of all possible districting plans is $\Plans$.

For an election $v$, we can tally the votes for each candidate; the candidate with the most votes wins.
Using potential outcomes notation, we denote the winner of voter $i$'s district under districting plan $q$ and election $v$ as $\win_i(v,q)$.

@@

The key intuition from Section \ref{sec:motivation} was that to be harmed by a decision a voter must have a better outcome in the counterfactual world where another decision was made.
To operationalize this, we need to have a counterfactual districting plan $\tilde q$.
Then we may define the *harm* to an individual $i$ in election $v$ held under districting plan $q$ as $$
h_i(v,q,\tilde q) = \ind\{v(i) \neq \win_i(v, q)\}
        \ind\{v(i) = \win_i(v, \tilde q)\},
$$that is, a voter is harmed only if they are not represented by the candidate of their choice under $q$ and they would have been represented by their chosen candidate under the counterfactual plan $\tilde q$.
Notice the fundamental asymmetry in this definition: $h_i(v,q,\tilde q)\neq h_i(v,\tilde q,q)$.
Exchanging the role of the enacted plan and the counterfactual will not simply flip the direction of our conclusion; in general, $q$ will harm some individuals versus $\tilde q$, and $\tilde q$ will harm a distinct set of individuals versus $q$.
A "symmetrized" version of $h_i(v,q,\tilde q)$ would have to combine both of these groups individuals: those harmed as well as those who gain by electing their chosen candidate under $q$ but not under the counterfactual $\tilde q$.
In practice, voters, courts, or politicians may care more about preventing harm than maximizing gains.

Our definition of harm is limited in two key regards.
First, it considers only individuals who vote; if a person abstains from voting then their calculated harm is zero.
A natural extension of this definition would be to separate an individual's candidate preference from their vote choice; the latter would be used in calculating election winners, but the former could provide a more broadly-based harm measure.
Naturally, this approach requires auxiliary data to implement (such as a large-scale survey), since candidate preferences for nonvoters cannot be directly inferred from election returns.

A second limitation is that $h_i(v,q,\tilde q)$ ignores any preferences a voter may have between candidates he or she did not vote for.
For example, a voter may consider candidates A and B nearly interchangeable, but may strongly dislike candidate C.
If the voter ultimately voted for candidate A, this harm measure makes no distinction between candidate B or candidate C winning the voter's district.
This reflects the simplistic nature of the cost function that is implicit in the harm measure.
The problem could be remedied by replacing the indicator functions with other cost functions that consider ordinal preferences.
Ballot-level ranked-choice vote data, or candidate ideology scores, could be used to estimate such a cost function.
Here, for simplicity and to avoid making further assumptions, we limit ourselves to the indicator-based cost function.
Section \ref{sec:boston} further discusses the implications of this particular specification in the context of primary elections.

@@

As defined above, $h_i(v,q,\tilde q)$ captures harm in a single election and relative to a single counterfactual districting plan $\tilde q$.
In general we will be interested in outcomes over multiple elections, and possibly a much larger set of counterfactual plans.
Ideally, we would like to be able to average individual harm over a set of future elections (under the same districting plan), or over a set of hypothetical districting plans which are consistent with districting criteria, or even over a set of individuals with some shared characteristic.

To allow for this, we replace the fixed election $v$, counterfactual districting plans $\tilde q$, and individual voter $i$ with random variables $V\in\Elecs$, $\tilde Q\in\Plans$, and $I\in\Voters$.
The random variable $V$ can be conceptualized as ranging over possible future elections---one realization might correspond to a heavily Democratic-favoring midterm year, while another might involve incumbents underperforming particularly badly.
The random variable $\tilde Q$ captures the range of potential counterfactual districting plans.
Rarely would an analyst have a single counterfactual plan in mind; different realizations of $\tilde Q$ correspond to different districting plans that are permissible under the relevant districting criteria.
Finally, $I$ is defined to be a voter taken uniformly at random from $\Voters$, with $I\indep V,\tilde Q$.

The randomness in $V$ and $\tilde Q$ allows us to compare the enacted districting plan to many plausible counterfactual alternatives, and across a range of electoral environments.
At times we may wish to study on a particular election or a particular counterfactual plan; treating $V$ and $\tilde Q$ as random variables allows us to condition on particular values of each.
A particular specification of the distribution of $V$ and $\tilde Q$ is required only when *estimating* our harm measures in a particular application, a topic we return to in Section \ref{sec:estimating}.

With these definitions, the harm for a (randomly selected) individual under plan $q$ can be written as $$
H(q) \dfeq h_I(V, q, \tilde Q).
$$$H(q)$ is itself a random variable, representing the harm to *some* individual in *some* election compared to *some* counterfactual plan.
The random variable $I$ here serves as a kind of "veil of ignorance" [@rawls2004theory]; a districting plan $q$ which tends to produce a low $H(q)$ would be expected to be preferred over a plan which tended to produce a higher $H(q)$.

$H(q)$ actually contains all the relevant information about the harm created by a plan $q$.
We can "zoom in" or summarize various aspects of the plan by conditioning on values of $V$, $\tilde Q$, and $I$, or by taking expectations.
Thus, for example, the harm for a single individual $i$ becomes $H(q)\mid I=i$; and the electorate's average harm in a particular election $v$ becomes$$
\E[H(q)\mid V=v] = \Pr[v(I)\neq\win_I(v, q)
    \text{ and }v(I)=\win_I(v, \tilde Q)],
$$that is, the probability that a randomly selected voter in this election is misrepresented under the adopted plan but would not have been under a randomly selected counterfactual.

@@

Single-member districts are often motivated by the value in representation to specific communities with shared interests; indeed, preserving "communities of interest" is one of the most common statutory and constitutional requirements imposed by states on the plan-drawing process [@ncslcriteria].
It is therefore natural to consider not just the average harm to voters done by a plan, but also how this harm is distributed across certain groups of voters, defined by race, party, or other attributes of interest.

@@

Fairness is a strict condition; any real-life plan will never be exactly fair.
To quantify deviations from fairness, we introduce the concept of *differential harm*, defined as $$
  \Delta_{G_k-G_l}H(q) \dfeq \E[H(q)\mid I\in G_k] - \E[H(q)\mid I\in G_l],
$$ for two groups $G_k$ and $G_l$.
So $\Delta_{G_k-G_l}H(q)$ will be positive if voters in group $G_k$ are harmed at a higher rate than voters in group $G_l$, indicating that plan $q$ favors $G_l$ over $G_k$.
Using our definition of fairness, $\Delta_{G_k-G_l}H(q)=0$ for all $G_k,G_l\in\Groups$ if and only if $q$ is fair.

@@

For example, the algorithms of @carter2019 and @mccartan2020 sample from the maximum-entropy distribution of districting plans which are geographically contiguous, have district populations within a deviation from equality, and which have a certain average compactness value (according to a particular graph-theoretic compactness measure).
These maximum-entropy distributions put as few conditions as possible on the districting sampling process, as long as a set of constraints imposed by the researcher are met.
If these constraints are precisely those which are required by law or traditional redistricting criteria, then samples from this distribution provide a natural set of counterfactual districting plans, uninfluenced by superfluous partisan considerations, to use in estimating $H(q)$ and $\Delta H(q)$.
In practice, the translation from tradition and law into mathematical formulations of constraints is not always clear or even well-defined; there is certainly an element of subjectivity in sampling a set of districting plans.
Nonetheless, sampling methods are widely used in practice [see e.g., @2019rucho; @2018league; @2022merrill; @becker2021computational; @chen:rodd:13].

@@

[^2]: For this, we use the baseline count of Democratic or Republican votes.
    This is a slight simplification, since because the vote share changes across random draws, the number of Democratic and Republican voters does, too.
    To deal with this issue completely necessitates modeling elections at the precinct level, which requires much more data and computational expenditure.

@@

A primary advantage of the proposed harm measures is that they are defined at the individual level, allowing for the study of redistricting far beyond racial and partisan gerrymandering.
However, the measures provide an improvement over existing analytic approaches in both of these important contexts.

@@

While the specific legal requirements for a vote dilution claim will obviously remain front-and-center for court challenges of racial gerrymanders, it is notable that the proposed harm measures unify all three *Gingles* criteria.
Criteria (b) and (c) captures the misrepresentation of minority voters by a candidate they do not support, while (a) requires the existence of a counterfactual where this would not be the case; together, (a) and (c) establish that minority voters are harmed.
But the proposed measures can also tackle trickier situations where the *Gingles* criteria may not be clearly met.

@@

We first examine the values of each metric on the two proposals alone.
The estimate of differential partisan harm aligns with the expected partisan skew of each plan, with a value of $-3.6\%$ for the Democratic proposal and $2.0\%$ for the Republican proposal.
These values are relatively directly interpretable; for example, the estimated differential harm of $-3.6\%$ means that an average Democratic voter is 3.6 percentage points less likely to be misrepresented than their average Republican counter-partisan.
The efficiency gap, declination, and partisan bias measures agree with the differential harm estimates in this regard, though the former two are much more discrete.
The efficiency gap and partisan bias estimate give roughly equal scores in absolute value to the Democratic and Republican plans, in comparison to differential harm and declination, which identify the Democratic proposal as slightly more extreme.
While the mean-median measure identifies the Republican proposal as favoring Republicans, it also scores the Democratic proposal as favoring the Republicans, albeit by less.

@@

We can also flip the setup and compute harm by averaging over the simulated plans and using the enacted plan as a counterfactual.
This will produce a different answer, since harm is not symmetric between the study plan and the counterfactual.
Comparing the enacted plan to the the simulations shows who is harmed by the current plan versus a race-neutral baseline; the reverse comparison shows who would be harmed by a race-neutral baseline in comparison to the current plan.
For this reverse comparison, along the first dimension, we estimate that a race-neutral baseline would differentially harm Black voters at a rate of 3.1% compared to the enacted plan Along the second dimension, the differential harm to Black voters would be 1.8%.

@@

We model the observed turnout $n_{jv}$ and vote counts $s_{jk}n_{jv}$ as \begin{align*}
    n_{jv} \mid \turn_{jr}, \beta^{(t)}_v
        &\sim \Binlog\qty(\vap_j, \logit(\turn_j^\top\vb p_j) + \beta^{(t)}_v) \\
    \logit(\turn_j) \mid \mu^{(t)}, \Sigma^{(t)}
        &\sim \Norm(\mu^{(t)}, \Sigma^{(t)}) \\
    s_{jv}n_{jv} \mid \supp_{jr}, \turn_{jr}, \beta^{(s)}_v
        &\sim \Binlog\qty(n_{jv}, \logit\qty(
        \supp_j^\top \frac{\turn_j\circ\vb p_j}{\turn_j^\top\vb p_j}) + \beta^{(s)}_v) \\
    \logit(\supp_j) \mid \mu^{(s)}, \Sigma^{(s)}
        &\sim \Norm(\mu^{(s)}, \Sigma^{(t)}),
\end{align*} where the $\vb*\beta^{(t)}$ and $\vb*\beta^{(s)}$ model election-specific logit shifts, $\Binlog$ indicates the Binomial distribution with the probability parameter specified on the logit scale, and $\circ$ indicates the elementwise (Hadamard) product.
We give $\vb*\beta^{(t)}$ an i.i.d. $\Norm(0, 0.6^2)$ prior,and $\vb*\beta^{(s)}$ an i.i.d. $\Norm(0, 0.4^2)$ prior, and $\mu^{(t)}$ an i.i.d. $\Norm(0, 1.5^2)$ prior.
We set priors independently on the variance and correlation components of $\Sigma^{(t)}$ and $\Sigma^{(s)}$; the former received $\Gam(1.5, 1.5/0.5)$ and $\Gam(1.5, 1.5/0.25)$ priors for turnout and support, while the latter received uniform priors (i.e., LKJ priors with shape parameter 1).
Several reparametrizations were made for computational efficiency; the full Stan code for the model is available as part of the replication code.

@@

We give $\vb*\beta^{(t)}$ an i.i.d. $\Norm(0, 0.5^2)$ prior,and $\vb*\beta^{(s)}$ an i.i.d. $\Norm(0, 4.0^2)$ prior, and $\logit(\mu^{(t)})$ an i.i.d. $\Beta(10, 30)$ prior.
We set priors independently on the variance and correlation components of $\Sigma^{(t)}$ and $\Sigma^{(p)}$; the former has $\Gam(1.5, 1.5/0.25)$ and $\Gam(1.5, 1.5/1.0)$ priors for turnout and support, while the latter have LKJ priors with shape parameters 4.0 and 20.0.
A larger LKJ shape parameter places more weight on correlation matrices closer to diagonal, i.e., it regularizes away from high correlations.
The scale parameters $\vb*\rho$ have i.i.d. $\Gam(1.5, 1.5/4.0)$ priors, the fudge factors $\vb*\alpha$ have i.i.d. $\Gam(5.0, 5.0)$ priors, and $\eps$ has an $\Expo(1/4.0)$ prior.
Overall, these priors weakly identify the location and scale of the parameters.
Several reparametrizations were made for computational efficiency; the full Stan code for the model is available as part of the replication code.

>>>>

We formalize and generalize the concepts in Section \ref{sec:motivation}, beginning with some notation.
Let $\Voters$ be the set of individuals, or voters, in the region and time period under consideration.
Individuals vote to select a candidate to represent each of a set of districts, indexed by $\Distrs$.

@@

Every voter resides in some legislative district.,
This assignment defines a *districting plan* and is represented here by a function $q(i)$ indicating the district that individual $i$ lives in.
The set of all possible districting plans is $\Plans$.

For an election $v$, we can tally the votes for each candidate and the candidate with the most votes wins.
Using potential outcomes notation, we denote the winner of voter $i$'s district under districting plan $q$ and election $v$ as $\win_i(v,q)$.

@@

The key intuition from Section \ref{sec:motivation} is that *to be harmed*, a voter must have a better outcome in the counterfactual world where a different decision was made.
To operationalize this, we need to have a counterfactual districting plan $\tilde q$.
Then we may define the *harm* to an individual $i$ in election $v$ held under districting plan $q$ as $$
h_i(v,q,\tilde q) = \ind\{v(i) \neq \win_i(v, q)\}
        \ind\{v(i) = \win_i(v, \tilde q)\},
$$that is, a voter is harmed only if they are not represented by the candidate of their choice under $q$ but they would have been represented by their candidate of choice under the counterfactual plan $\tilde q$.
Notice the fundamental asymmetry in this definition: $h_i(v,q,\tilde q)\neq h_i(v,\tilde q,q)$.
Exchanging the role of the enacted plan and the counterfactual will not simply flip the direction of our conclusion.
In general, $q$ will harm some individuals while $\tilde q$, and $\tilde q$ will harm a different set of individuals.
A symmetric version of $h_i(v,q,\tilde q)$ would need to combine both of these groups: those harmed and those who gain by electing their chosen candidate under $q$ but not under the counterfactual $\tilde q$.
In practice, voters, courts, or politicians may find different balances in preventing harm and maximizing gains.

Our definition of harm is limited in two key regards.
First, it considers only individuals who vote: people who abstain from voting have a harm of zero.
A natural extension of this definition is to separate individual candidate preference from vote choice. 
The latter defines election winners, but the former provides a more-broad harm measure.
Naturally, this approach requires auxiliary data to implement, such as a large-scale survey, as candidate preferences for non-voters are not directly inferred from election returns.

A second limitation is that $h_i(v,q,\tilde q)$ ignores any preferences a voter may have between the candidates that he or she did not vote for.
For example, a voter may consider candidates A and B nearly interchangeable, but may strongly dislike candidate C.
If the voter ultimately voted for candidate A, this harm measure makes no distinction between candidate B or candidate C winning the voter's district.
This reflects the simplistic nature of the cost function assumed in single-choice elections.
The problem could be remedied by replacing the indicator functions in the harm measure with other cost functions that consider ordinal preferences.
Ballot-level ranked-choice vote data, or candidate ideology scores, could be used to estimate such a cost function.
Here, for simplicity and to avoid making further assumptions, we focus on the indicator-based cost function.
Section \ref{sec:boston} further discusses the implications of this particular specification, in the context of primary elections.

@@

As defined above, $h_i(v,q,\tilde q)$ captures harm in a single election and relative to one counterfactual districting plan $\tilde q$.
In general, we are interested in outcomes over multiple elections and a much larger set of counterfactual plans.
Ideally, we would average individual harm (1) over a set of future elections under the enacted districting plan and (2) over a set of hypothetical districting plans which are consistent with districting criteria.
We could even consider a set of individuals with some shared characteristic(s).

To allow for this, we replace the fixed election $v$, counterfactual districting plans $\tilde q$, and individual voter $i$ with random variables $V\in\Elecs$, $\tilde Q\in\Plans$, and $I\in\Voters$.
The random variable $V$ can be conceptualized as ranging over possible future elections---one realization could correspond to a heavily Democratic-favoring midterm year, while another could involve incumbents underperforming particularly badly.
The random variable $\tilde Q$ captures the range of potential counterfactual districting plans.
Rarely would an analyst have a single counterfactual plan in mind.
Different realizations of $\tilde Q$ correspond to different districting plans that are permissible under the relevant districting criteria.
Finally, $I$ is defined to be a voter taken uniformly at random from $\Voters$, with $I\indep V,\tilde Q$.

The randomness in $V$ and $\tilde Q$ allows us to compare the enacted districting plan to many plausible counterfactual alternatives, and across a range of electoral environments.
At times we may wish to study on a particular election or a particular counterfactual plan.
If we treat $V$ and $\tilde Q$ as random variables, we can then condition on particular values of each.
A particular specification of the distribution of $V$ and $\tilde Q$ is required only when *estimating* our harm measures in a particular application, a topic we return to in Section \ref{sec:estimating}.

With these definitions, the harm for a (randomly selected) individual under plan $q$ can be written as 
$$H(q) \dfeq h_I(V, q, \tilde Q).$$

$H(q)$ is itself a random variable, representing the harm to *some* individual in *some* election compared to *some* counterfactual plan.
The random variable $I$ here serves as a kind of "veil of ignorance" [@rawls2004theory]: a districting plan $q$ which tends to produce a low $H(q)$ would be expected to be preferred over a plan which tended to produce a higher $H(q)$.

$H(q)$ describes the harm created by a plan $q$.
We can zoom in to specific dimensions of the plan by conditioning on values of $V$, $\tilde Q$, and $I$, or by taking expectations.
Thus, for example, the harm for a single individual $i$ becomes $H(q)\mid I=i$; and the electorate's average harm in a particular election $v$ becomes

$$\E[H(q)\mid V=v] = \Pr[v(I)\neq\win_I(v, q) \text{ and }v(I)=\win_I(v, \tilde Q)],$$
    that is, the probability that a randomly selected voter in this election is misrepresented under the adopted plan but would not have been under a randomly selected counterfactual.

@@

Single-member districts are often motivated by the value in representation to specific communities with shared interests.
Indeed, preserving "communities of interest" is one of the most common statutory and constitutional requirements imposed by states on the plan-drawing process [@ncslcriteria].
It is therefore natural to consider not just the average harm to voters done by a plan, but also how this harm is distributed across certain groups of voters, defined by race, party, or other attributes of interest.

@@

Fairness is a strict condition: real-life plans are incredibly unlikely to be exactly fair.
To quantify deviations from fairness, we introduce the concept of *differential harm*, defined as $$
  \Delta_{G_k-G_l}H(q) \dfeq \E[H(q)\mid I\in G_k] - \E[H(q)\mid I\in G_l],
$$ for two groups $G_k$ and $G_l$.
So $\Delta_{G_k-G_l}H(q)$ will be positive if voters in group $G_k$ are harmed at a higher rate than voters in group $G_l$, indicating that plan $q$ favors $G_l$ over $G_k$.
Using our definition of fairness, $\Delta_{G_k-G_l}H(q)=0$ for all $G_k,G_l\in\Groups$ if and only if $q$ is fair.

@@

For example, the algorithms of @carter2019 and @mccartan2020 sample from the maximum-entropy distribution of districting plans which are geographically contiguous, have district populations within a deviation from equality, and which have a certain average compactness value (according to a particular graph-theoretic compactness measure).
These maximum-entropy distributions put as few conditions as possible on the districting sampling process, as long as a set of constraints imposed by the researcher are met.
If these constraints are precisely those which are required by law or traditional redistricting criteria, then samples from this distribution provide a natural set of counterfactual districting plans, uninfluenced by superfluous partisan considerations, to use in estimating $H(q)$ and $\Delta H(q)$.
In practice, the translation from tradition and law into mathematical formulations of constraints is not always clear or even well-defined.
There is certainly an element of subjectivity in sampling a set of districting plans.
Nonetheless, sampling methods are widely used in practice [see e.g., @2019rucho; @2018league; @2022merrill; @becker2021computational; @chen:rodd:13].

@@

[^2]: For this, we use the baseline count of Democratic or Republican votes.
    This is a slight simplification, since the vote share changes across random draws, the number of Democratic and Republican voters changes too.
    To deal with this issue completely necessitates modeling elections at the precinct level, which requires more data and computational costs.

@@

A primary advantage of our proposed harm measures is that they our measures are defined at the individual level.
This allows for the study of redistricting far beyond racial and partisan gerrymandering.
The measures provide an improvement over existing analytical approaches in both of these important contexts.

@@

While the specific legal requirements for a vote dilution claim will obviously remain front-and-center for court challenges of racial gerrymanders, it is notable that the proposed harm measures unify all three *Gingles* criteria.
Criteria (b) and (c) capture the misrepresentation of minority voters by a candidate they do not support, while (a) requires the existence of a counterfactual where this would not be the case and (a) and (c) together establish that minority voters are harmed.
But the proposed measures can also tackle trickier situations where the *Gingles* criteria may not be clearly met.

@@

We first examine the values of each metric on the two proposals alone.
The estimate of differential partisan harm aligns with the expected partisan skew of each plan, with a value of $-3.6\%$ for the Democratic proposal and $2.0\%$ for the Republican proposal.
These values are relatively directly interpretable.
For example, the estimated differential harm of $-3.6\%$ means that an average Democratic voter is 3.6 percentage points less likely to be misrepresented than their average Republican counter-partisan.
The efficiency gap, declination, and partisan bias measures agree with the differential harm estimates in this regard, though the former two are much more discrete.
The efficiency gap and partisan bias estimate give roughly equal scores in absolute value to the Democratic and Republican plans, in comparison to differential harm and declination, which identify the Democratic proposal as slightly more extreme.
While the mean-median measure identifies the Republican proposal as favoring Republicans, it also scores the Democratic proposal as favoring the Republicans, albeit by less.

@@

We can also flip the setup and compute harm by averaging over the simulated plans and using the enacted plan as a counterfactual.
This will produce a different answer, since harm is not symmetric between the study plan and the counterfactual.
Comparing the enacted plan to the the simulations shows who is harmed by the current plan versus a race-neutral baseline.
The reverse comparison shows who would be harmed by a race-neutral baseline in comparison to the current plan.
For this reverse comparison, along the first dimension, we estimate that a race-neutral baseline would differentially harm Black voters at a rate of 3.1% compared to the enacted plan Along the second dimension, the differential harm to Black voters would be 1.8%.

@@

We model the observed turnout $n_{jv}$ and vote counts $s_{jk}n_{jv}$ as \begin{align*}
    n_{jv} \mid \turn_{jr}, \beta^{(t)}_v
        &\sim \Binlog\qty(\vap_j, \logit(\turn_j^\top\vb p_j) + \beta^{(t)}_v) \\
    \logit(\turn_j) \mid \mu^{(t)}, \Sigma^{(t)}
        &\sim \Norm(\mu^{(t)}, \Sigma^{(t)}) \\
    s_{jv}n_{jv} \mid \supp_{jr}, \turn_{jr}, \beta^{(s)}_v
        &\sim \Binlog\qty(n_{jv}, \logit\qty(
        \supp_j^\top \frac{\turn_j\circ\vb p_j}{\turn_j^\top\vb p_j}) + \beta^{(s)}_v) \\
    \logit(\supp_j) \mid \mu^{(s)}, \Sigma^{(s)}
        &\sim \Norm(\mu^{(s)}, \Sigma^{(t)}),
\end{align*} where the $\vb*\beta^{(t)}$ and $\vb*\beta^{(s)}$ model election-specific logit shifts, $\Binlog$ indicates the Binomial distribution with the probability parameter specified on the logit scale, and $\circ$ indicates the elementwise (Hadamard) product.
We give $\vb*\beta^{(t)}$ an i.i.d. $\Norm(0, 0.6^2)$ prior,and $\vb*\beta^{(s)}$ an i.i.d. $\Norm(0, 0.4^2)$ prior, and $\mu^{(t)}$ an i.i.d. $\Norm(0, 1.5^2)$ prior.
We set priors independently on the variance and correlation components of $\Sigma^{(t)}$ and $\Sigma^{(s)}$. 
The former received $\Gam(1.5, 1.5/0.5)$ and $\Gam(1.5, 1.5/0.25)$ priors for turnout and support, while the latter received uniform priors (i.e., LKJ priors with shape parameter 1).
Several reparametrizations are made for computational efficiency.
The full Stan model is included in the replication code.

@@

We give $\vb*\beta^{(t)}$ an i.i.d. $\Norm(0, 0.5^2)$ prior,and $\vb*\beta^{(s)}$ an i.i.d. $\Norm(0, 4.0^2)$ prior, and $\logit(\mu^{(t)})$ an i.i.d. $\Beta(10, 30)$ prior.
We set priors independently on the variance and correlation components of $\Sigma^{(t)}$ and $\Sigma^{(p)}$.
The former has $\Gam(1.5, 1.5/0.25)$ and $\Gam(1.5, 1.5/1.0)$ priors for turnout and support, while the latter have LKJ priors with shape parameters 4.0 and 20.0.
A larger LKJ shape parameter places more weight on correlation matrices closer to diagonal, i.e., it regularizes away from high correlations.
The scale parameters $\vb*\rho$ have i.i.d. $\Gam(1.5, 1.5/4.0)$ priors, the fudge factors $\vb*\alpha$ have i.i.d. $\Gam(5.0, 5.0)$ priors, and $\eps$ has an $\Expo(1/4.0)$ prior.
Overall, these priors weakly identify the location and scale of the parameters.
Several reparametrizations were made for computational efficiency.
The full Stan code for the model is available as part of the replication code.
